The problem and promise of scale in multilayer animal social networks

### 2020-02-14 paper/manuscript.Rmd
update winpos discussion

, showing decreasing connectivity in shifted winter time windows and  greater connectivity in summer layers at later window positions.
Moving winter and summer seasons showed increasing connectivity of individuals. Graph strength and layer relevance increased at time window position ~20 for summer layers (Figure \@ref(fig:winpos)a, Figure \@ref(fig:winpos)b). Layer similarity... <!-- TODO: between
seasons increased consistently across landcover class (Figure
\@ref(fig:winlen)b).--> Connective redundancy was stable throughout the shifting window positions (Figure \@ref(fig:winpos)). Similar to window length, increasing window position results in a mismatch between expected periods of resource seasonality and corresponding sociality.

>>>>

Moving window positions defining seasons showed an increase in connectivity of
individuals in summer layers. Graph strength increased at time window position
~20 for summer and winter layers  and, while summer layers continued to
increase, winter layers showed a decrease in graph strength at time window
position ~35 (Figure \@ref(fig:winpos)a). Layer relevance increased across
moving window positions for summer layers and was relatively stable for winter
layers (Figure \@ref(fig:winpos)b). These results indicate slight decreasing
connectivity and increased connectivity in summer layers at shifted winter time
windows. Layer similarity was relatively stable across moving window positions
except for a sharp decline at window position ~28 in forage and open layers
(Figure \@ref(fig:winpos) c). Connective redundancy showed a marginal increase
with increasing window position (Figure \@ref(fig:winpos) d). Similar to window
length, changing the position of the time window in this case results in a
mismatch between expected periods of resource seasonality and corresponding
sociality, highlighting the importance of carefully selecting temporal scale of
analysis.
